Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-27 writeup/gz_hubble_data.tex
Bands in SDSS 2.5 are not primed; that's the old USNO.

%The creation of 51,861 images from these sources is described in Section
%\ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites created using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522~galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
\stripe{} images and matched to a co-add source. This resulted in a total
set of 30,339~images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in the same manner as previous
iterations of Galaxy~Zoo.

@@

In order to test and correct for the effects of redshift, GZH includes a set of
calibration images.  These are simulated images of a set of nearby galaxies as
they would appear observed at a variety of redshifts.  The input images are
from the SDSS \citep{yor00,str02}.  The sample consists of 288~nearby galaxies
at $z<0.013$. The galaxies spanned a variety of morphologies (as selected by
GZ2 classifications, including identifications of spiral structure,
ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
$r^\prime$-band surface brightnesses.  The overall selection spanned the
redshift range of SDSS targets and maximized the number of \hst{} galaxies at
the same surface brightness and redshift (Figure~\ref{fig:sb_redshift}).  The
\ferengi{} code was used to produce sets of images corresponding to
observations of these galaxies out to $z_\mathrm{sim}=1.0$ (see
Section~\ref{ssec:ferengi}).  The resulting images were classified in the GZH
interface using the standard classification scheme.

@@

The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. The combination of all
such parameters forms a high-dimensional space, and it is not clear how to
separate this into individual effects. Instead, the method used here employs
only two parameters as a simple model of the effect of redshift brightness on classification: the
$i^\prime$-band surface brightness ($\mu_\mathrm{i}$; intrinsic) and redshift ($z$;
extrinsic).

>>>>

%The creation of 51,861 images from these sources is described in Section
%\ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r$-band Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
21,522~galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
\stripe{} images and matched to a co-add source. This resulted in a total
set of 30,339~images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels \citep{nie04}. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in the same manner as previous
iterations of Galaxy~Zoo.

@@

In order to test and correct for the effects of redshift, GZH includes a set of
calibration images.  These are simulated images of a set of nearby galaxies as
they would appear observed at a variety of redshifts.  The input images are
from the SDSS \citep{yor00,str02}.  The sample consists of 288~nearby galaxies
at $z<0.013$. The galaxies spanned a variety of morphologies (as selected by
GZ2 classifications, including identifications of spiral structure,
ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
$r$-band surface brightnesses.  The overall selection spanned the
redshift range of SDSS targets and maximized the number of \hst{} galaxies at
the same surface brightness and redshift (Figure~\ref{fig:sb_redshift}).  The
\ferengi{} code was used to produce sets of images corresponding to
observations of these galaxies out to $z_\mathrm{sim}=1.0$ (see
Section~\ref{ssec:ferengi}).  The resulting images were classified in the GZH
interface using the standard classification scheme.

@@

The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. The combination of all
such parameters forms a high-dimensional space, and it is not clear how to
separate this into individual effects. Instead, the method used here employs
only two parameters as a simple model of the effect of redshift brightness on classification: the
$i$-band surface brightness ($\mu_\mathrm{i}$; intrinsic) and redshift ($z$;
extrinsic).
